DLISA: Distributed Learning-based \\ Intelligent Service Agents

### 2014-12-01 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

In recent work communities of web services have been proposed that facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed. The first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. These solutions suffer from two main issues: 1) The solutions consider a centralized manager for communities and most of the decision making process for communities happens at a centralized entity. The problem is in real world scenarios most service providers work in distributed settings and having a centralized entity making decisions is not very feasible. 2) Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work of sub-communities instead of calculating the complex shapely-value gain distribution method. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

In this paper, we introduce DLISA (Distributed Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. This model works in distributed manner in which our services are self-sufficient in decision making process and do not rely on a centralized decision maker process. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

In further detail, DLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DLISA have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -3.851432 & - & 6.969072 & -3.851432 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}

>>>>

In recent work communities of web services have been proposed that facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed. The first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. These solutions suffer from two main issues: 
\begin{enumerate}
	\item The solutions consider a centralized manager for communities and most of the decision making process for communities happens at a centralized entity. The problem is in real world scenarios most service providers work in distributed settings and having a centralized entity making decisions is not very feasible. 
	\item The solutions propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy, for each time services or communities adopt an strategy. Or the problem is reduced by eliminating important parameters.
\end{enumerate}
Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work of sub-communities instead of calculating the complex shapely-value gain distribution method. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

In this paper, we introduce DLISA (Distributed Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
The training model utilizes web services with enough information to efficiently decide and predict the outcome of their moves amongst the available services accessible to them. This model works in distributed manner in which our services are self-sufficient in decision making process and do not rely on a centralized decision maker process. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

In further detail, DLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots. Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DLISA have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}
